---
title: Statistical analysis
subtitle: Bioacoustics stimuli for L2 learning
author: <a href="http://researcher.website.com/">Researcher name</a>
date: "`r Sys.Date()`"
toc: true
toc-depth: 4
toc-location: left
number-sections: true
highlight-style: pygments
format:
  html:
    df-print: kable
    code-fold: true
    code-tools: true
    css: qmd.css
editor_options: 
  chunk_output_type: console
---

```{r set root directory, echo = FALSE}

# set working directory 
knitr::opts_knit$set(root.dir =  "..")

```

```{r add link to github repo, echo = FALSE, results='asis'}

# print link to github repo if any
if (file.exists("./.git/config")){
  config <- readLines("./.git/config")
  url <- grep("url",  config, value = TRUE)
  url <- gsub("\\turl = |.git$", "", url)
  cat("\nSource code and data found at [", url, "](", url, ")", sep = "")
  }

```

```{r setup style, echo = FALSE, message = FALSE, warning=FALSE}

# options to customize chunk outputs
knitr::opts_chunk$set(
  tidy.opts = list(width.cutoff = 65), 
  tidy = TRUE,
  message = FALSE
 )

```


<!-- skyblue box -->

::: {.alert .alert-info}

# Purpose {.unnumbered .unlisted}

- The first goal of this report

- The second goal of this report

:::

&nbsp; 


<!-- light brown box -->
::: {.alert .alert-warning}

# Report overview {.unnumbered .unlisted}

- You can have the sections listed here, for instance:

  - [Lorem ipsum](#lorem-ipsum)
  - [Takeaways](#takeaways)

:::

&nbsp;

# Analysis flowchart {.unnumbered .unlisted}
```{mermaid, fig.align = "center"}
flowchart
  A[Read data] --> B(Format data) 
  B --> C(Graphs)
  C --> D(Statistical analysis)
  D --> E(Model summary) 

style A fill:#44015466
style B fill:#3E4A894D
style C fill:#26828E4D
style D fill:#6DCD594D

```


# Load packages {.unnumbered .unlisted}

```{r load packages}

# knitr is require for creating html/pdf/word reports
# formatR is used for soft-wrapping code

# install/ load packages
sketchy::load_packages(packages = c("lme4", "psych", "sjPlot", "corrplot", "readxl", "Hmisc", "brms", "emmeans", "viridis"))

source("~/Dropbox/R_package_testing/brmsish/R/helpers.R")
source("~/Dropbox/R_package_testing/brmsish/R/extended_summary.R")
```

# Read data
```{r, warning=FALSE}

dat_day_1 <- read_excel("./data/raw/UCREA_day1_R.xlsx")

dat_day_2_online <- read_excel("./data/raw/UCREA_day2_LDT_R (2).xlsx", sheet = "Day 2_no_fillers_LDT")

dat_day_3_online <- read_excel("./data/raw/UCREA_day3_LDT_Acu_FINAL (1).xlsx")

dat_day_2_pldt <- read_excel("./data/raw/PLDT_day2RT_processed (1).xlsx")

dat_day_3_pldt <- read_excel("./data/raw/PLDT_day3_R_FINAL (1).xlsx", sheet = "Data")

```



# Regression models

## Recognition

```{r, eval = FALSE, warning=F, message=F, echo=T}

dat_day_1$condition_f <- factor(as.character(dat_day_1$Condition))
dat_day_1$ID <- factor(as.character(dat_day_1$ID))

levels(dat_day_1$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_1$L1_f <- factor(as.character(dat_day_1$L1))

levels(dat_day_1$L1_f) <- c("Native", "Non-native")

dat_day_1$vocab_sc <- scale(dat_day_1$vocab)

priors <- c(prior(normal(0, 4), class = "b"))
priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_recognition <- brm(formula = Recog ~ condition_f * L1_f + vocab_sc + (1 | ID) + (1 | nonword), family = bernoulli(), iter = 5000, chains = chains, cores = chains, data = dat_day_1, backend = "cmdstanr", file = "./data/processed/regression_model_day_1_recognition", prior = priors)

mod_recall <- brm(formula = Recall ~ condition_f * L1_f + vocab_sc + (1 | ID) + (1 | nonword), family = bernoulli(), iter = 5000, chains = chains, cores = chains, data = dat_day_1, backend = "cmdstanr", file = "./data/processed/regression_model_day_1_recall", prior = priors)
```

```{r, warning=F, message=F, echo=T, results='asis'}
mod_recognition <- readRDS("./data/processed/regression_model_day_1_recognition.rds")

extended_summary(fit = mod_recognition, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

### Contrasts

#### Full table
```{r, warning=F, message=F, echo=T, results='asis'}
contrasts_recognition <- as.data.frame(emmeans(mod_recognition, pairwise ~ condition_f * L1_f)$contrasts)

names(contrasts_recognition)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(contrasts_recognition, highlight = TRUE, fill = viridis(10)[7])

print(coef_table)
```

#### Subset native vs non-native
```{r, warning=F, message=F, echo=T, results='asis'}
contrasts_recognition$first <- sapply(strsplit(contrasts_recognition$contrast, " - "), "[[", 1)
contrasts_recognition$second <- sapply(strsplit(contrasts_recognition$contrast, " - "), "[[", 2)

contrasts_recognition <- contrasts_recognition[!grepl("Non-native", contrasts_recognition$first) & grepl("Non-native", contrasts_recognition$second), ]

coef_table <- html_format_coef_table(contrasts_recognition[, 1:4], highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```

## Recall
```{r, eval = FALSE, warning=F, message=F, echo=T}

dat_day_1$condition_f <- factor(as.character(dat_day_1$Condition))
dat_day_1$ID <- factor(as.character(dat_day_1$ID))

levels(dat_day_1$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_1$L1_f <- factor(as.character(dat_day_1$L1))

levels(dat_day_1$L1_f) <- c("Native", "Non-native")

dat_day_1$vocab_sc <- scale(dat_day_1$vocab)

priors <- c(prior(normal(0, 4), class = "b"))
priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_recall <- brm(formula = Recall ~ condition_f * L1_f + vocab_sc + (1 | ID) + (1 | nonword), family = bernoulli(), iter = 5000, chains = chains, cores = chains, data = dat_day_1, backend = "cmdstanr", file = "./data/processed/regression_model_day_1_recall", prior = priors)
```

```{r, results='asis'}
mod_recall <- readRDS("./data/processed/regression_model_day_1_recall.rds")

extended_summary(fit = mod_recall, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

### Contrasts

#### Full table
```{r, results='asis'}
constrasts_recall <- as.data.frame(emmeans(mod_recall, pairwise ~ condition_f * L1_f)$contrasts)

names(constrasts_recall)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(constrasts_recall[, 1:4], highlight = TRUE, fill = viridis(10)[7])

print(coef_table)
```

#### Subset native vs non-native
```{r, results='asis'}
constrasts_recall$first <- sapply(strsplit(constrasts_recall$contrast, " - "), "[[", 1)
constrasts_recall$second <- sapply(strsplit(constrasts_recall$contrast, " - "), "[[", 2)

constrasts_recall <- constrasts_recall[!grepl("Non-native", constrasts_recall$first) & grepl("Non-native", constrasts_recall$second), ]

coef_table <- html_format_coef_table(constrasts_recall[, 1:4], highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```

## LDT

### Day 2
```{r, eval = FALSE, warning=F, message=F, echo=T}

str(dat_day_2_online)

dat_day_2_online$condition_f <- factor(as.character(dat_day_2_online$Condition))
levels(dat_day_2_online$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_2_online$relate_f <- factor(as.character(dat_day_2_online$Relate))
levels(dat_day_2_online$relate_f) <- c("Related", "Unrelated", "Nonword")

dat_day_2_online$ID <- factor(as.character(dat_day_2_online$ID))

dat_day_2_online$L1_f <- factor(as.character(dat_day_2_online$L1))

levels(dat_day_2_online$L1_f) <- c("Native", "Non-native")

dat_day_2_online$vocab_sc <- scale(dat_day_2_online$Vocab)

dat_day_2_online$recall_f <- factor(as.character(dat_day_2_online$Recall))

levels(dat_day_2_online$recall_f) <- c("No", "Yes")

priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_LDT <- brm(formula = RT ~ L1_f + condition_f + vocab_sc + relate_f + recall_f +(1 | ID) + (1 | prime), family = lognormal(), iter = 5000, chains = chains, cores = chains, data = dat_day_2_online, backend = "cmdstanr", file = "./data/processed/regression_model_day_2_LDT", prior = priors)

```

```{r, warning=F, message=F, echo=T, results='asis'}
mod_LDT <- readRDS("./data/processed/regression_model_day_2_LDT.rds")

extended_summary(fit = mod_LDT, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

#### Contrasts

```{r, warning=F, message=F, echo=T, results='asis'}

contrasts_LDT <- as.data.frame(emmeans(mod_LDT, pairwise ~ condition_f)$contrasts)

names(contrasts_LDT)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(contrasts_LDT, highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```

### Day 3
```{r, eval = FALSE, warning=F, message=F, echo=T}

str(dat_day_3_online)

dat_day_3_online$condition_f <- factor(as.character(dat_day_3_online$Condition))
levels(dat_day_3_online$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_3_online$relate_f <- factor(as.character(dat_day_3_online$Relate))
levels(dat_day_3_online$relate_f) <- c("Related", "Unrelated", "Nonword")

dat_day_3_online$ID <- factor(as.character(dat_day_3_online$ID))

dat_day_3_online$L1_f <- factor(as.character(dat_day_3_online$L1))

levels(dat_day_3_online$L1_f) <- c("Native", "Non-native")

dat_day_3_online$vocab_sc <- scale(dat_day_3_online$Vocab)

dat_day_3_online$recall_f <- factor(as.character(dat_day_3_online$Recall))

levels(dat_day_3_online$recall_f) <- c("No", "Yes")


priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_LDT <- brm(formula = RT ~ L1_f + condition_f + vocab_sc + relate_f + recall_f +(1 | ID) + (1 | prime), family = lognormal(), iter = 5000, chains = chains, cores = chains, data = dat_day_3_online, backend = "cmdstanr", file = "./data/processed/regression_model_day_3_LDT", prior = priors)

```

```{r, warning=F, message=F, echo=T, results='asis'}
mod_LDT <- readRDS("./data/processed/regression_model_day_3_LDT.rds")

extended_summary(fit = mod_LDT, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

#### Contrasts

```{r, warning=F, message=F, echo=T, results='asis'}

contrasts_LDT <- as.data.frame(emmeans(mod_LDT, pairwise ~ condition_f)$contrasts)

names(contrasts_LDT)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(contrasts_LDT, highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```


## PLDT

### Day 2
```{r, eval = FALSE, warning=F, message=F, echo=T}

str(dat_day_2_pldt)

dat_day_2_pldt$condition_f <- factor(as.character(dat_day_2_pldt$Condition))
levels(dat_day_2_pldt$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_2_pldt$relate_f <- factor(as.character(dat_day_2_pldt$Related))
levels(dat_day_2_pldt$relate_f) <- c("Related", "Unrelated", "Nonword")

dat_day_2_pldt$ID <- factor(as.character(dat_day_2_pldt$ID))

dat_day_2_pldt$L1_f <- factor(as.character(dat_day_2_pldt$L1))

levels(dat_day_2_pldt$L1_f) <- c("Native", "Non-native")

dat_day_2_pldt$vocab_sc <- scale(dat_day_2_pldt$Vocab)

dat_day_2_pldt$recall_f <- factor(as.character(dat_day_2_pldt$Recall))

levels(dat_day_2_pldt$recall_f) <- c("No", "Yes")

priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_PLDT2 <- brm(formula = RT ~ L1_f + condition_f + vocab_sc + relate_f + recall_f +(1 | ID) + (1 | prime), family = lognormal(), iter = 5000, chains = chains, cores = chains, data = dat_day_2_pldt, backend = "cmdstanr", file = "./data/processed/regression_model_day_2_PLDT", prior = priors)

```

```{r, warning=F, message=F, echo=T, results='asis'}
mod_PLDT2 <- readRDS("./data/processed/regression_model_day_2_PLDT.rds")

extended_summary(fit = mod_PLDT2, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

#### Contrasts

```{r, warning=F, message=F, echo=T, results='asis'}

contrasts_PLDT <- as.data.frame(emmeans(mod_PLDT2, pairwise ~ condition_f)$contrasts)

names(contrasts_PLDT)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(contrasts_PLDT, highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```

### Day 3
```{r, eval = FALSE, warning=F, message=F, echo=T}

str(dat_day_3_pldt)

dat_day_3_pldt$condition_f <- factor(as.character(dat_day_3_pldt$Condition))
levels(dat_day_3_pldt$condition_f) <- c("Linguistic", "Bioacoustic", "Combined")

dat_day_3_pldt$relate_f <- factor(as.character(dat_day_3_pldt$Relate))
levels(dat_day_3_pldt$relate_f) <- c("Related", "Unrelated", "Nonword")

dat_day_3_pldt$ID <- factor(as.character(dat_day_3_pldt$ID))

dat_day_3_pldt$L1_f <- factor(as.character(dat_day_3_pldt$L1))

levels(dat_day_3_pldt$L1_f) <- c("Native", "Non-native")

dat_day_3_pldt$vocab_sc <- scale(dat_day_3_pldt$VocabularyTest)

dat_day_3_pldt$recall_f <- factor(as.character(dat_day_3_pldt$Recall))

levels(dat_day_3_pldt$recall_f) <- c("No", "Yes")


priors <- c(
  # Prior for the intercept
  prior(normal(0, 10), class = Intercept),
  
  # Priors for the regression coefficients
  prior(normal(0, 2.5), class = b),
  
  # Prior for the group-level standard deviations (if applicable)
  prior(exponential(1), class = sd)
)

chains  <- 4 

mod_LDT <- brm(formula = RT ~ L1_f + condition_f + vocab_sc + relate_f + recall_f +(1 | ID) + (1 | prime), family = lognormal(), iter = 5000, chains = chains, cores = chains, data = dat_day_3_pldt, backend = "cmdstanr", file = "./data/processed/regression_model_day_3_PLDT", prior = priors)

```

```{r, warning=F, message=F, echo=T, results='asis'}
mod_PLDT3 <- readRDS("./data/processed/regression_model_day_3_PLDT.rds")

extended_summary(fit = mod_PLDT3, highlight = TRUE, remove.intercepts = TRUE,
            print.name = FALSE)
```

#### Contrasts

```{r, warning=F, message=F, echo=T, results='asis'}

contrasts_PLDT3 <- as.data.frame(emmeans(mod_PLDT3, pairwise ~ condition_f)$contrasts)

names(contrasts_PLDT3)[3:4] <- c("l-95% CI", "u-95% CI")

coef_table <- html_format_coef_table(contrasts_PLDT3, highlight = TRUE, fill = viridis(10)[7])

print(coef_table)

```

::: {.alert .alert-success}

# Takeaways {.unnumbered .unlisted}


::: 

&nbsp;

<!-- '---' adds a gray vertical line -->

---

&nbsp; 
 
 <!-- add packages used, system details and versions  -->
 
# Session information {.unnumbered .unlisted}

```{r session info, echo=F}

sessionInfo()

```
