---
title: "UCREA_day1"
author: "VerónicaGC"
date: '2024-05-31'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(lme4)
library (foreign)
library (reshape)
library (arm)
library (psy)
library (car)
library (plyr)
library (psychometric)
library (ICC)
library (ppcor)
library (Hmisc)
library (lm.beta)
library (GeneNet)
library (psych)
library(sjPlot)
library(stargazer)
library(dplyr)
library(tidyverse)
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
library(mice)


#Read in data file



library(readxl)
UCREA_day1<- read_excel("2024/UCREA_day1_R.xlsx")
View(UCREA_day1)


#Normality Recognition 
```{r warning=F, message=F, echo=T}
describe(UCREA_day1$Recog)
hist(UCREA_day1$Recog) #normal

#Normality Recall

describe(UCREA_day1$Recall)
hist(UCREA_day1$Recall) #normal

#GLM Recogntion
Recog=glm(Recog~Condition*L1+vocab,data=UCREA_day1,family="binomial")
summary(Recog)
tab_model(Recog)

#Correlations
```{r warning=F, message=F, echo=T}
my_data <- UCREA_day1[, c(2,14,19,21)]
head(my_data, 19)

co <- rcorr(as.matrix(my_data), type= c("pearson"))
co

#GLM Recall

Recall=glm(Recall~Condition*L1+vocab,data=UCREA_day1,family="binomial")
summary(Recall)
tab_model(Recall)


#Correlations
```{r warning=F, message=F, echo=T}
my_data1 <- UCREA_day1[, c(2,14,19,20)]
head(my_data1, 19)

co1 <- rcorr(as.matrix(my_data1), type= c("pearson"))
co1


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
