---
title: "LDTs_UCREA"
output: html_document
date: "2024-04-12"
---

---
title: "UCREA_day2_lexical"
author: "Verónica García-Castro"
date: "11/6/2023"
output: html_document
---

```{r setup, include=FALSE}
library(lme4)
library (foreign)
library (reshape)
library (arm)
library (psy)
library (car)
library (plyr)
library (psychometric)
library (ICC)
library (ppcor)
library (Hmisc)
library (lm.beta)
library (GeneNet)
library (psych)
library(sjPlot)
library(stargazer)
library(dplyr)
library(tidyverse)
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
library(mice)
```

## R Markdown

#Read in data file

library(readxl)
UCREA_day2_LDT_Acu <- read_excel("UCR2023/Publications/UCREA_day2_LDT_Acu_R.xlsx")
UCREA_day2_LDT_Acu


#Normality Accuracy 
```{r warning=F, message=F, echo=T}
describe(UCREA_day2_LDT_Acu$Accuracy)
hist(UCREA_day2_LDT_Acu$Accuracy) #normal


#GLM Accuracy
Accu=glm(Accuracy~Relate+L1+Condition,data=UCREA_day2_LDT_Acu,family="binomial")
summary(Accu)
tab_model(Accu)
```
#Read in new data file

```{r warning=F, message=F, echo=T}

UCREA_day2_LDT <- read_excel ("C:/Users/veronica.garcia/Downloads/UCREA_day2_LDT_R (2).xlsx")
View(UCREA_day2_LDT)
UCREA_day2_LDT
```
# normality RTs
```{r warning=F, message=F, echo=T}
describe(UCREA_day2_LDT$RT)
hist(UCREA_day2_LDT$RT) 

# transform to log to improve normalitY
UCREA_day2_LDT$RT_lg <- log10(max(UCREA_day2_LDT$RT + 1) -  UCREA_day2_LDT$RT)

#Check normality after transformation 

hist(UCREA_day2_LDT$RT_lg)  
```
# normality Vocab

```{r warning=F, message=F, echo=T}
describe(UCREA_day2_LDT$Vocab)
hist(UCREA_day2_LDT$Vocab) 

# transform to log to improve normalitY
UCREA_day2_LDT$Vocab_lg <- log10(max(UCREA_day2_LDT$Vocab + 1) -  UCREA_day2_LDT$Vocab)

#Check normality after transformation 

hist(UCREA_day2_LDT$Vocab_lg)
```
#Correlations
```{r warning=F, message=F, echo=T}
UCREA_day2_LDT
my_data <- UCREA_day2_LDT[, c(2,5,7,9)]
head(my_data, 2)

co <- rcorr(as.matrix(my_data), type= c("pearson"))
co
```
#Regression Model (Predictors: L1, Vocab_lg, Relate, Condition)

```{r warning=F, message=F, echo=T}
model1 <- lmerTest::lmer(RT_lg ~ L1+ Condition + Vocab_lg + Relate + Recall +(1 | ID) + (1 | prime),  data= UCREA_day2_LDT)
summary(model1)
tab_model(model1)
confint(model1, method="Wald", level=0.95)

#Assumptions
rstandard(model1)
durbinWatsonTest(model1) 
mean(vif(model1))
vif(model1) 
plot(model1)
```
#LDT DAY 3

```{r warning=F, message=F, echo=T}

UCREA_day3_LDT_Acu <- read_excel ("C:/Users/Admin/Downloads/UCREA_day3_LDT_Acu_FINAL (1).xlsx")

View(UCREA_day3_LDT_Acu)

# normality Accuracy
```{r warning=F, message=F, echo=T}
describe(UCREA_day3_LDT_Acu$Accuracy)
hist(UCREA_day3_LDT_Acu$Accuracy) 

#GLM Accuracy
Accu1=glm(Accuracy~Relate+L1+Condition,data=UCREA_day3_LDT_Acu, family="binomial")
summary(Accu1)
tab_model(Accu1)
```
#New dataset

```{r warning=F, message=F, echo=T}
library(readxl)
UCREA_day3_LDT <- read_excel("C:/Users/veronica.garcia/Downloads/UCREA_day3_LDT_R_FINAL.xlsx")
UCREA_day3_LDT
```

#normality RTs
```{r warning=F, message=F, echo=T}
# normality RTs
```{r warning=F, message=F, echo=T}
describe(UCREA_day3_LDT$RT)
hist(UCREA_day3_LDT$RT)

# transform to log to improve normalitY
UCREA_day3_LDT$RT_lg <- log10(max(UCREA_day3_LDT$RT + 1) -  UCREA_day3_LDT$RT)

#Check normality after transformation 

hist(UCREA_day3_LDT$RT_lg)  #use
```
#normality Vocab

```{r warning=F, message=F, echo=T}
describe(UCREA_day3_LDT$Vocab)
hist(UCREA_day3_LDT$Vocab) 

# transform to log to improve normalitY
UCREA_day3_LDT$Vocab_lg <- log10(max(UCREA_day3_LDT$Vocab + 1) -  UCREA_day3_LDT$Vocab)

#Check normality after transformation 

hist(UCREA_day3_LDT$Vocab_lg). # use
```
#Correlations

```{r warning=F, message=F, echo=T}

#Correlations
```{r warning=F, message=F, echo=T}

my_data1<- UCREA_day3_LDT[, c(2,3,4,7,11)]
head(my_data1,2)

co <- rcorr(as.matrix(my_data1), type= c("pearson"))
co
```
#Regression Mode1l (Predictors: L1, Vocab, Relate, Condition)

`{r warning=F, message=F, echo=T}
model2 <- lmerTest::lmer(RT_lg ~ L1 + Vocab_lg + Relate + Condition + (1 | ID) + (1 | prime),  data= UCREA_day3_LDT)
summary(model2)
tab_model(model2)
confint(model2, method="Wald", level=0.95)

#Assumptions
rstandard(model2)
durbinWatsonTest(model2) 
mean(vif(model2))
vif(model2) 
plot(model2)

